How to compute the fusion product of MV cycles in type A

### 2021-04-02 draft.tex
relevant fact from AM

    Exercise 2.20 from \cite{atiyah2018introduction}: If $f : A \to B$ is a ring homomorphism and $M$ is a flat $A$-module, then $M_B = B\otimes_A M$ is a flat $B$-module. Take $A=\CC[t]$ and $B=\CC\xt$. \marginpar[]{*}
\end{proof}

>>>>

    Exercise 2.20 from \cite{atiyah2018introduction}: If $f : A \to B$ is a ring homomorphism and $M$ is a flat $A$-module, then $M_B = B\otimes_A M$ is a flat $B$-module. Take $A=\CC[t]$ and $B=\CC\xt$. \marginpar[]{*}

    This exercise is irrelevant. We want to say something about two different modules over the same base ring. As Roger reminded the relevant fact is \cite[Proposition~10.14]{atiyah2018introduction}: 
    % 
    \begin{quotation}
        If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
    \end{quotation}
    applied to $A = \CC[t]$ and $\fa = (t)$. 
\end{proof}
